Distributed Multi-Heuristic A* (HAMSTAR)

### 2014-12-11 paper.tex
results stuff

\begin{figure}
\centering \includegraphics[width=3in]{pseudocode}
\caption{Pseudocode from Aine et al., detailing the original sequential version of the algorithm we parallelized.}
\label{fig:pseudocode}
\end{figure}

@@

Nevertheless, figure \ref{fig4} displays what the results might look like in a problem where the heuristic takes longer to calculate. Specifically, we artificially slow the heuristic calculation by a factor of 10. The result is that fewer states are expanded per second, and thus the cost of communicating a state is much lower relative to the cost of expanding it. In this case, our distributed algorithm can leverage the benefit of additional cores to outperform SMHA* if we use the one-on-one communication method described earlier in this paper. Thus, a distributed approach may prove helpful in domains such as manipulator arm planning, in which expansions are slowed by the collision checking and numerical integration needed to compute successor states and heuristics.

@@

In this paper we outlined the details of a distributed version of the SMHA* algorithm. We detailed the structure of the algorithm, and presented experimental results comparing the performance of the algorithm while varying a number of parameters. We also compared its performance to the original SMHA* algorithm. Although we found that in the specific domain we tested on (the sliding tile puzzle) our distributed variant did not outperform the original algorithm, we provided evidence that our algorithm could outperform SMHA* in domains where heuristics are difficult to calculate, or in general where state expansion is expensive.
% TODO: Fill me in!

@@

%\section{Final Paper Outline}

@@

\begin{figure}
\centering
\includegraphics[width=1.6in]{graphs/hamstar}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{subfigure}{3in}
  \includegraphics[width=3in]{pseudocode}
  \caption{Pseudocode}
  \label{fig1}
\end{subfigure}
\begin{subfigure}{2in}
  \includegraphics[width=2in]{graphs/puzzle}
  \caption{15-puzzle goal configuration}
  \label{fig2}
\end{subfigure}
\caption{Pseudocode from Aine et al., detailing the original sequential version of the algorithm we parallelized, alongside the sliding tile puzzle which we use it to solve.}
\label{fig:pseudocode}
\end{figure}

@@

Nevertheless, figure \ref{fig4} displays what the results might look like in a problem where the heuristic takes longer to calculate. Specifically, we artificially slow the heuristic calculation by a factor of 10. The result is that fewer states are expanded per second, and thus the cost of communicating a state is much lower relative to the cost of expanding it. In this case, our distributed algorithm can leverage the benefit of additional cores to outperform SMHA* if we use the one-on-one communication method described earlier in this report. Thus, a distributed approach may prove helpful in domains such as manipulator arm planning, in which expansions are slowed by the collision checking and numerical integration needed to compute successor states and heuristics.

@@

In this report, we outlined the details of a distributed version of the SMHA* algorithm. We detailed the implementation of the algorithm, and presented experimental results comparing its performance while varying a number of parameters. We also compared its performance to the original SMHA*. Although we found that our distributed variant did not outperform the original SHMA* in the specific domain we tested on (the sliding tile puzzle), we provided evidence that our algorithm could outperform SMHA* in domains where heuristics are difficult to calculate, or in general where state expansion is expensive.
% TODO: Fill me in!

@@

%\section{Final Report Outline}

@@

\begin{figure}[b]
\centering
\includegraphics[width=1.6in]{graphs/hamstar}
\end{figure}
